---
title: "cavega_OriginalHomeworkCode_04"
author: "C. Vega"
date: "10/15/2019"
output: html_document
---
# This is [Homework 04](https://fuzzyatelin.github.io/bioanth-stats/homework-04.html)
## There are two parts to this homework, one is writing your own function and the other is pulling from the [Kamilar and Cooper Dataset]("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")

# Five Challenges
1. I started with question 2 and got stuck at multiple parts. I struggled most with trying to figure out how to add the equation to the plot, how to create the confidence intervals and PI.
2. I need to get better at navigating ggplot2, since I really can't quite get the hang of it. 
3. In writing the function I got stuck many times. I looked through the textbooks, modules, and searched online without really understanding what each piece of code was supposed to do. 
4. Part of my issue with writing the function is not being able to translate the homework expectations to specific code.
5. Are there any resources you suggest for better understanding if/else statements?


# Part 1: Write  A Function
## Use If- else function
```{r}
Practice
  dude <- function(x) {ifelse(x=="dude","dude","*blank stare*")} 
  dude("yo")

```
## Beginning to Write the Function
```{r}
z.prop.test <- function(p1, n1, p2, n2, p0, alternative = "two.sided", conf.level = 0.95)
   z.statistic <- {
     if (pl == 0){
       return(0)}
        else{{if(is.null(p2) & is.null(n2))
                  if((n1 * p1 <5) | (n1 * (1-p1) < 5))
                  return(c("Warning: Not a Normal Distribution", (p1-p0) /sqrt((p0* (1-p0))/ n1)))
                  else(return(p1-p0)/ sqrt((p0 * (1-p0))/n1))}
          
          {if(!!is.null(p2) & !!is.null(n2))
            if ((p1== 0) | (p2== 0)) {
              return(0)}
            else {if((n1 * p1 < 5) | (n1 * (1-p1) < 5) | (n2 * p2 <5) | (n2 * (1-p2) < 5))
            return(c("Warning: Not a Normal Distribution", ((p1 - p2 - p0 / sqrt((p0 *(1-p0))/((1/n1) + (1 /n2)))))))}
          else(return(((p1-p2-p0) / sqrt((p0 * (1- p0))/ ((1/n1) + (1/n2))))))}}
}

convert.z.score <- function(z.statistic, one.sided=NULL) {
  if(is.null(one.sided)){
    pval = pnorm(-abs(z.statistic));
    pval = 2 * pval
  } else if(one.sided=="-") {
    pval = pnorm(z.statistic);
  } else {
    pval = pnorm(-z.statistic);
    return(pval);
  }
return(c(z.statistic, convert.z.score))
}
  
z.prop.test
```

# Part 2: 
## We will start with part 2, per Dr. Schmitt's suggestion in order to get ego boost before writing a function. 
```{r}
# Loading in Data
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
## Creating a linear regression for longevity to brain size
```{r}
library("ggplot2")

plot(data=d, MaxLongevity_m~Brain_Size_Species_Mean) #quick plot to look at relationship

LModel <- lm(MaxLongevity_m~Brain_Size_Species_Mean, data=d )
LModel #model to use with the graph

names(LModel)

#Equation: y=1.218x+248.952

# Finding correlation value for the two
cor(d$MaxLongevity_m, d$Brain_Size_Species_Mean, use= "complete.obs")
  ## Looking for the number of values that do not have both of these 
      incomplete <- which(is.na(d$MaxLongevity_m)|is.na(d$Brain_Size_Species_Mean))

      length(incomplete) # number of NAs removed from the dataset


```
## Creating Linear Regression Plot for Longevity to Brain size
```{r}

g <- ggplot(data = d, aes(x = MaxLongevity_m, y = Brain_Size_Species_Mean)) 
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g <- g + geom_text(aes(label = paste(d, sep = "")),
  parse = TRUE)
g <- g + geom_text() + annotate("text", label = "y=1.218x+248.952", x=200, y=200)
g


plot(fitted(LModel), residuals(LModel))
hist(residuals(LModel))
qqnorm(residuals(LModel))

# Confidence interval

confint(LModel, level=0.90)





```

## Creating a linear regression plot for log longevity to log brain size
```{r}
g <- ggplot(data = d, aes(x = MaxLongevity_m, y = Brain_Size_Species_Mean))
g <- g + geom_point()
g <- g + geom_point(aes(x = MaxLongevity_m, y = Brain_Size_Species_Mean), colour = "red")
g <- g + geom_segment(aes(x = MaxLongevity_m, y = Brain_Size_Species_Mean, xend = MaxLongevity_m, yend = Brain_Size_Species_Mean))
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g

```

## Peer Commentary: Good Job!

1. I get this error message when I try to run your plot "g" on line 101 -> "Error: Aesthetics must be either length 1 or the same as the data (213): label". For my plot, I did x= mean brain size and y= max longevity, you did the opposite way around. I switched yours just to see if it would help this error message but it didn't. Maybe look into this error message on google. I think its suggesting that your data "d", which has 213 rows, needs to match what you put in your aes() function.
  + Also, try putting the information you put in annotate() function on line 100 actually in your geom_text() function parantheses. I used ?plotmath to find appropriate syntax for the equation since you can't just write it out as y=1.218x+248.952 (you need to use % and ==)

2. For your plot "g" on lines 120-125, you say you're doing it for the Log LR but in your aes() function, you don't plot the Log(mean brain size) and Log(max longevity), you just plot the regular data. Did you mean to do this? 

3. I used the predict() function both for putting my PI onto the plot and for producing PI's for longevity when brain size = 800 (question 4). Try looking into predict() and how I used it in my code to help you with these! (not 100% sure if what I did is right though lol..)

4. When you use geom_smooth() while you're making a plot in ggplot2, it automatically plots 95% CI. Since the question asks for 90%, you just need to specifiy this in your geom_smooth(). So -> geom_smooth(method= lm, level= 0.90).

5. On Line 30 in your function, you wrote if pl == 0. Did you mean to write pl or p1? 

6. It's difficult for me to comment on your function in Part 1 becuase I know there are probably so many different ways to write the function so I can't be sure what is right and wrong. Especially since I'm not confident with mine so it's hard to advise you. Hopefully we can review it all together in class! 